State and Parameter Estimation for a Spatio-temporal Neural Field Model

### 2010-04-14 ltx/Journal of Neuroengineering/IOPLaTeXGuidelines.tex
switching to different sty for journal

\title[Author guidelines for IOP journals in  \LaTeXe]{How to prepare and submit an article for 
publication in an IOP journal using \LaTeXe}

\author{Author's name}

\address{Institute of Physics 
Publishing, Dirac
House, Temple Back, Bristol BS1 6BE, UK}
\ead{custserv@iop.org}
\begin{abstract}
This document describes the  preparation of an article using \LaTeXe\ and 
\verb"iopart.cls" (the IOP \LaTeXe\ preprint class file).
This class file is designed to help 
authors produce preprints in a form suitable for submission to any of the
journals published by Institute of Physics Publishing.
Authors submitting to any IOP journal, i.e.\ 
both single- and double-column ones, should follow the guidelines set out here. 
On acceptance, their TeX code will be converted to 
the appropriate format for the journal concerned.

>>>>

\title[State and Parameter Estimation for a Spatio-temporal Neural Fields]{State and Parameter Estimation for a Spatio-temporal Neural Field Model}

\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}

\address{$^1$ Department
of Electrical and Electronic Engineering, University of Melbourne, Melbourne,
Vic, 3010 Australia}
\address{$^2$ Department
of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield,
S1 3JD, UK}
\address{$^3$ Mike's}
\address{$^4$ Ken's}
\ead{dfreestone@bionicear.org}
\begin{abstract}
This document describes the  preparation of an article using \LaTeXe\ and 
\verb"iopart.cls" (the IOP \LaTeXe\ preprint class file).
This class file is designed to help 
authors produce preprints in a form suitable for submission to any of the
journals published by Institute of Physics Publishing.
Authors submitting to any IOP journal, i.e.\ 
both single- and double-column ones, should follow the guidelines set out here. 
On acceptance, their TeX code will be converted to 
the appropriate format for the journal concerned.
